Self recovering capabilities in images using the BPCS Steganography algorithm

### 2014-08-27 Paper/main.tex
Added a description of terms

\fi
\tableofcontents

>>>>

\fi
\tableofcontents
\section{Terms used}
This paper makes use of several terms and acronyms.
This section serves to make the meaning of those terms clear.

\begin{itemize}
  \item Original Image: This refers to the original image without any modifications.
  \item Image after embedding: This refers to the the original image after the embedding process has been applied.
  \item Image after reconstruction: This refers to the reconstructed version of the original image that was obtained by applying the reconstruction process to the image after embedding.
  \item LSB: This refers to the least significant bit in a binary string.
  \item MSB: This refers to the most significant bit/bits in a binary string.
  \item Section, Image section, Pixel section: This refers to a section 8x8 pixels in an image.
  \item Block: This refers to an individual bit plane of a specific section of the image. There are 8 such blocks in each section since each pixel is represented by 8 bits for each colour. 
\end{itemize}
